\section{Basic definitions}
Formally: extract semantic
and geometric information
from an image.


\begin{enumerate}
    \item Semantic information
          \begin{enumerate}
              \item What objects are in the image?
              \item Who is the person?
              \item What is the person doing?
          \end{enumerate}
    \item Geometric information
          \begin{enumerate}
              \item Where are objects in the image?
              \item How far is the person from me?
              \item What is the shape of the car?
              \item In what direction is the car moving?
              \item Eyes of AI
          \end{enumerate}
\end{enumerate}


goal of computer vision
• Compute the 3D shape of the world
• Recognize objects and people
• Improve photos (“Computational Photography”)


Challenges of computer vision
Viewpoint variation
Illumination
Scale
Intra-class variation (elements of the same class can vary a lot (example in the class of ferraris there are newer and older models))
Motion (The subject in the image might be moving fast)
Occlusion (The subject in the immage might be partially hidden behind other objects)
Background clutter (Difficult to distinguish the subject form a cluttery background)



Computer vision uses knowledge from
physics
math
Statistical learning

Related fields are
image processing
computer graphics


\section{Image filtering}
What is an image
• A grid (matrix) of intensity values

grayscale image: 1 matrix
RGB image: 3 matrices

(common to use one byte per value: 0 = black, 255 = white)
1 byte per color means 24 bits that are 16ml colors

Since 2d images are projections of 3d images there is a loss of information. To rebuild the 3d scenario we need additional prior information on the context or structure of the world


We can think of a (grayscale, continuous)
image as a function, f, from R2 to R:
f (x,y) gives the intensity at position (x,y)


A digital image is a discrete (sampled, quantized)
version of this function

quantization is lossy

As with any function, we can apply operators to
an image

\subsection{Convolutional filter (Linear filtering)}
Is a transformation

